### 2020-06-01 paper.tex
Add First Subsection of Simulated Annealing

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage[OT1]{fontenc}
\usepackage{xcolor}
\usepackage{pgfplots}
\pgfplotsset{compat=1.9}

@@

@@

At the end of each iteration, the temperature value decreases by multiplying it by a cooling factor which is less than $1$. This process iterates until the temperature goes below $1$. It is clear that the performance of this algorithm is based upon four parameters:

    \begin{itemize}
        \item Initial configuration 
        \item Move generation function
        \item Cost function 
        \item Annealing schedule
    \end{itemize}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows, shapes.gates.logic.US, calc}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage[OT1]{fontenc}
\usepackage{xcolor}
\usepackage{pgfplots}
\pgfplotsset{compat=1.9}

@@

\newcommand\T{\rule{0pt}{2.6ex}}       % Top strut
\newcommand\B{\rule[-1.2ex]{0pt}{0pt}} % Bottom strut

@@

At the end of each iteration, the temperature value decreases by multiplying it by a cooling factor which is less than $1$. This process iterates until the temperature goes below $1$. It is clear that the performance of this algorithm is based upon four parameters\slash steps:

\subsubsection{Initial Configuration}
In this step, the individual cells are extracted from the circuit and for each cell, the inputs and outputs are determined. The following diagram and table show the circuit is decomposed.
\begin{figure}[!h]
    \centering
    \begin{tikzpicture}[thick, scale = 2]
        \node[and gate US, draw, rotate=0, logic gate inputs=nn] at (0,1) (and1) {1};
        \node[and gate US, draw, rotate=0, logic gate inputs=nn] at (0,0) (and2) {2};
        \node[or gate US, draw, rotate=0, logic gate inputs=nn] at ($(and2) + (1.5, 0.5)$) (or1) {3};

        \draw ($(and1.input 1) + (-0.5, 0)$) -- (and1.input 1);
        \draw ($(and1.input 2) + (-0.5, 0)$) -- (and1.input 2);
        \draw ($(and2.input 1) + (-0.5, 0)$) -- (and2.input 1);
        \draw ($(and2.input 2) + (-0.5, 0)$) -- (and2.input 2);

        \draw (and1.output) -- ([xshift=0.5cm]and1.output) |- (or1.input 1);
        \draw (and2.output) -- ([xshift=0.5cm]and2.output) |- (or1.input 2);

        \draw (or1.output) -- ++ (0.5,0);
    \end{tikzpicture}
    \caption{Sample circuit diagram}
\end{figure}

\begin{table}[H]
    \caption{Sample Cells Data}
    \centering
     \begin{tabular}{||c c c||} 
     \hline
     \textit{\textbf{Cell}} & \textit{\textbf{Input}} & \textit{\textbf{Output}} \T \B \\ 
     \hline
     \hline
     1 & - & 3 \T \B \\ 
     \hline
     2 & - & 3 \T \B \\
     \hline
     3 & 2 & - \T \B \\
     \hline
     \end{tabular}
     \label{table1}
\end{table}

At this step, the total wirelength of cells interconnections will most likely be large due to them being placed randomly. Hence the presence of the rest of the subsequent procedures which aim to achieve the optimal placement of the cells.

\subsubsection{Move Generation Function}
\subsubsection{Cost Function}
\subsubsection{Annealing Schedule}
